---
title: "Aggregating already annotated miRNAs"
date: '(`r format(Sys.time(), format = "%Y-%m-%d")`)'
output:
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    social: menu
    source_code: embed
    theme: cosmo
    self_contained: no
---

```{css}
.correct:before {
  content: '\2611';
  color: #008100;
  font-style:normal;
  font-weight:bold;
  font-size: 150%;

}
.incorrect:before {
  content: '\2612';
  font-style:normal;    
  color: #b20610;
  font-size: 150%;
}

 .zoom {
  height:400px;
	display:block;
  left: 50%;
  margin: auto;
  border: 0
} 

```

```{r setup, include = FALSE}
library(DT)
library(dplyr)
library(tibble)
library(formattable)
knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE,
                      warning = FALSE)

options(stringsAsFactors = F)
options(digits=3)
premirTab <- read.table("Translate_out.txt", sep = "\t", header = T)
premirTab <- premirTab[, -ncol(premirTab)]
premirTab <- cbind(premirTab, Delete="<button class=\"btnDelete\">Delete</button>")
linkname <- gsub(":", "_", premirTab[,2])
premirTab[,1] <- paste0("<a href=\"javascript:void(0)\" onclick=\"mirnaplot('",linkname,"')\">", premirTab[,1],"</a>")
dbsum <- sum(colnames(premirTab)%in%c("miRBase", "PmiREN", "sRNAanno", "Psgenes", "sRNA_Seq"))
dbloc <- ncol(premirTab)-dbsum-1

for(numt in (dbloc+1):(ncol(premirTab)-1)){
  premirTab[,numt] <- factor(premirTab[,numt], levels = unique(premirTab[,numt]))
}

premirTab <- premirTab[,c(1,4,dbloc:ncol(premirTab))]


```

Results  {data-orientation=columns data-icon="fa-area-chart"}
================================

There are three sections in this HTML report. In **Overview and Summary Information**, we list the aggregated miRNAs that identified by four databases and small RNA-seq data. By clicking on the link in the table, the **RNAfold** and **CentroidFold** sections interactively show the RNA structure of RNAfold and CentroidFold prediction.

Column 1 {data-width=400}
-------------------------------------

### Overview and Summary Information 

```{r outdata}
premirTab <- premirTab %>% rowid_to_column("Row") %>% mutate(Row = "")
premirTab$Mature_arm <- factor(premirTab$Mature_arm, levels = unique(premirTab$Mature_arm))

datatable(
    premirTab,
    elementId = "linktable",
    class="compact cell-border",
    filter = 'top',
    extensions = c("Select", "Buttons", 'ColReorder'),
    options = list(
        autoWidth = TRUE,
        dom = 'Bfrtip',
        buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
        columnDefs = list(list(className = "select-checkbox",targets = 0, orderable = FALSE),
                          list(width = '2px', targets = "_all")),
        select = list(style = "multi", selector = "td:first-child"),
        searchHighlight = TRUE,
        colReorder = FALSE,
        scrollX = TRUE,
        fixedColumns = FALSE,
        extensions = 'Responsive',
        pageLength = 20),
    escape = FALSE,
    rownames = FALSE,
    callback = JS("$('#linktable tbody').on('click','.btnDelete',function(){table.row( $(this).parents('tr') ).remove().draw();});"))%>%
  formatStyle(TRUE, `text-align` = 'center')
```
<p style="font-size:14px;"> The table displays a collection of miRNAs from public databases and small RNA-Seq data. `Precursors`: The name of miRNA precursors; `pLen`: The length of miRNA precusors; `miRBase/PmiREN/sRNAanno/Psgenes`: Whether miRNAs are included in these databases. TRUE means being included, and NO means no; `sRNA_Seq`: Whether miRNAs are predicted in small RNA-Seq data (sRNA-Seq). </p>


Column 2 {data-width=200}
--------------------------------------------

### RNAfold

```{r RNAfold}
library(htmltools)
tags$img(id="content1",class="zoom", src=knitr::image_uri(paste0("png/", linkname[1], "_r.png")))
```

### CentroidFold

```{r CentroidFold}
library(htmltools)
tags$img(id="content2",class="zoom", src=knitr::image_uri(paste0("png/", linkname[1], "_c.png")))
```

```{js}
function mirnaplot(event)
{
document.getElementById("content1").src= "png/" + event + "_r.png";
document.getElementById("content2").src= "png/" + event + "_c.png";
}
```
