---
title: "Detailed representations of ath-MIR156b"
output:
    flexdashboard::flex_dashboard:
        orientation: rows
        vertical_layout: scroll
        social: menu
        source_code: embed
        theme: cosmo
        self_contained: no
---

```{r setup, include=FALSE}
library(DT)
library(purrr)
library(readr)
library(dplyr)
library(cytoscape)
library(kableExtra)
library(highcharter)
library(svgPanZoom)
options(stringsAsFactors = F)
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)
```

```{r import, include=FALSE}
info_table_raw <- read.table("final_table.txt", sep = "\t", header = T)
info_table <- info_table_raw[,c(2,5:37)]
info_table <- info_table[info_table$ID!="", ]

tissue_info <- read.table("sample_info.txt", sep = "\t", stringsAsFactors = F, row.names = 1)
mature_exp <- read.table("miRNA_in_sample.txt", sep = "\t", stringsAsFactors = F, row.names = 1)
rownames(mature_exp) <- gsub("T", "U", rownames(mature_exp))

tmp_fullname <- info_table$Stem_loop_loc
tmp_fullname <- gsub(":", "-", tmp_fullname)
tmp_index_value <- which(tmp_fullname%in%"xxxxxx")

for(tmp_index in tmp_index_value){
  tmp_name <- info_table[tmp_index, 2]
  info_vec <- info_table[tmp_index, c(1:13,20:21)]
  
  tmp_df <- data.frame("Location"=as.character(info_vec[c(2,5,7,10)]), 
                       "Sequence"=as.character(info_vec[c(3,6,8,11)]), 
                       "Length"=as.character(c(info_vec[4],  nchar(info_vec[6]), 
                                               info_vec[c(9,12)])))
  rownames(tmp_df) <- c("miRNA precursors", "Stem loop", "5p", "3p")
  mature_df <- t(mature_exp[c(info_vec$Seq5p, info_vec$Seq3p), ])
  mature_df[is.na(mature_df)] <- 0
  arm_ratio <- apply(mature_df, 1, function(x){
    if(max(x[1:2])<3){
      return(0)
    } else{
      if(info_vec$Mature_arm == '5p'){
        return(round(log2((x[1]+1)/(x[2]+1)), 2))
      } else{
        return(round(log2((x[2]+1)/(x[1]+1)), 2))
      }
    }
  })
}
```

```{css}
p.seq {
    white-space: nowrap;
    overflow: hidden;
    text-overflow: ellipsis;
    width: 800px;
    min-width: 0;
    margin: 0;
    font-size: 15px;
}

p.seq:hover {
    overflow: none;
    width: auto;
}

p.one{
  margin-top:0.2em;
}
```

Browse {data-icon=fa-area-chart}
=====================================

  &emsp;**In order to better elucidate each miRNA, this page contains the following parts: 1. miRNA sequences; 2. prediction structure; 3. read mapping in miRNA precursor; 4. miRNA expression and arm selection in different samples; 5. miRNA-target interactions; 6. miRNA isoforms**

Row 
-------------------------------------

### Location and sequence {data-width=250}

```{r table1, results='asis'}
eseq <- tmp_df[1,2]
eseqms <- regexpr(tmp_df[3,2], eseq)[1]
eseqss <- regexpr(tmp_df[4,2], eseq)[1]

tmp_df[1,2] <- paste0('<p class="seq">', substr(eseq, 1, eseqms-1),'<span style="background-color: #F88017">',
       tmp_df[3,2], "</span>", substr(eseq, eseqms+nchar(tmp_df[3,2]), eseqss-1),
       '<span style="background-color: #168EF7">', tmp_df[4,2], "</span>", substr(eseq, eseqss+nchar(tmp_df[4,2]), nchar(eseq)), '</p>')

tmp_df[2,2] <- paste0('<p class="seq"><span style="background-color: #F88017">',
       tmp_df[3,2], "</span>", substr(eseq, eseqms+nchar(tmp_df[3,2]), eseqss-1),
       '<span style="background-color: #168EF7">', tmp_df[4,2], "</span></p>")

knitr::kable(tmp_df, escape = FALSE) %>%kable_styling("striped", full_width = TRUE)
```

## {data-height=10}

<p class="one"></p>

Row
-------------------------------------

### RNAfold structure {data-height=100, data-width=350}

```{r pressure1, echo=FALSE, fig.cap="RNAfold", out.width = '33%'}
svgPanZoom::svgPanZoom( read_file(paste0("data/",  gsub(":", "_", tmp_name), '_r.svg')))
```

### Centroidfold structure {data-width=350}

```{r pressure2, echo=FALSE, fig.cap="Centroidfold", out.width = '33%'}
svgPanZoom::svgPanZoom( read_file(paste0("data/",  gsub(":", "_", tmp_name), '_c.svg')))
```

### Information {data-width=250}

```{r}
fold_info <- t(read.table(paste0("data/", tmp_name, '_fold.txt')))
colnames(fold_info) <- c("RNAfold", "Centriodfold")
rownames(fold_info) <- c("miRNAs", "meet criterion", "mismatch+bugleOne", "bugleOne", "bugleTwo")
knitr::kable(fold_info, escape = FALSE, align = "c") %>% 
  kable_styling("striped", full_width = TRUE)
```

## {data-height=10}

<p class="one"></p>

Row
-----------------------------------

### Overview of read-stacks on extended miRNA precursor  {data-height=150}

<div style="height:100%;width:100%;overflow:auto">
```{r readstacks, class="scroll-100", results='asis'}
htmltools::includeHTML(paste0("./data/", tmp_name, '_map.html'))
```
</div>

## {data-height=10}

<p class="one"></p>

Row
-------------------------------------

### mature miRNA expression

```{r}
tissue_name <- tissue_info[rownames(mature_df),]
exp_df <- data.frame("miRNAs"=rep(c(paste0(info_vec[1], "-5p"), paste0(info_vec[1], "-3p")), each=nrow(mature_df)), "TPM" = c(mature_df[,1], mature_df[,2]), "Tissues"= rep(tissue_name, 2), stringsAsFactors = F)
exp_df <- exp_df[exp_df[,3]!="-", ]
exp_df[,1] <- factor(exp_df[,1], levels = unique(exp_df[,1]))

hcboxplot(x = exp_df$TPM, var = exp_df$Tissues, var2 = exp_df$miRNAs, outliers = FALSE, 
          color = c("#DE3025", "#257ADE")) %>%
  hc_chart(type = "column") %>% 
  hc_xAxis(title = list(text = "")) %>% 
  hc_yAxis(title  = list(text = "TPM")) %>% 
  hc_exporting(enabled = TRUE, filename = "mature_miRNA_expression")
```

### Arm switch events

```{r}
mature_df_out <- data.frame('5p'=mature_df[,1], 
                            '3p'=mature_df[,2], "ratio"= arm_ratio, "grouplist"=tissue_info[rownames(mature_df),], stringsAsFactors = F)
mature_df_out <- mature_df_out[mature_df_out[,4]!="-", ]
mature_df_out <- mature_df_out[order(mature_df_out[["ratio"]], decreasing = T), ]
mature_df_out <- mature_df_out[order(mature_df_out[,3], decreasing=T), ]
mature_df_out <- mature_df_out[order(mature_df_out[,4]), ]

hchart(
  mature_df_out, 
  "scatter",
  hcaes(x=1:nrow(mature_df_out), y=ratio, group = grouplist, radius = 0), radius = 10
  ) %>% 
  hc_xAxis(title = list(text = "")) %>% 
  hc_yAxis(title  = list(text = "Log2(miR/miR*)")) %>% 
  hc_tooltip(
    pointFormat = "{series.name}: <b>{point.y}</b><br/>", 
    shared = TRUE,
    valueSuffix = "", 
    crosshairs = TRUE
  ) %>% 
  hc_add_theme(hc_theme_flat(chart = list(backgroundColor = "#FFF")))%>% 
  hc_exporting(enabled = TRUE, filename = "Arm_switch_events")
```

## {data-height=10}

<p class="one"></p>

Row {.tabset}
--------------------------------------------

### Network of miRNAs-target interactions {data-width=400}

```{r}
tmp_path <- paste0(info_table[tmp_index_value, 5], ".mti")
if(file.exists(tmp_path)){
    inputRaw <- read.table(tmp_path, sep = "\t", header = F, stringsAsFactors = F)
    cat(paste0(info_table[tmp_index_value, 5], ".mti"), "\n")
    if(nrow(inputRaw)>0){
      gene_description <- read.table("gene_description.txt", row.names = 1, stringsAsFactors = F, sep = "\t")
      
      inputRaw[,2] <- gsub("\\.\\d", "", inputRaw[,2])
      inputRaw[,4] <- gene_description[inputRaw[,2], 1]
      inputRaw <- unique(inputRaw[grepl(info_vec$ID, inputRaw[,1]), c(1:4,11)])
      
      colnames(inputRaw)[1:5] <- c("miRNA Acc.", "Target Acc.", "Expect", "Target description", "Inhibition")
      inputRe <- unique(inputRaw[,1:2])
      
      
      nodes <- data.frame(id = unique(c(inputRe[,1],inputRe[,2])))%>%
            mutate(node_color = ifelse(id %in% inputRe[,1],
                                   "#DE3025",
                                   "#85C7E6"),
                   node_shape = ifelse(id %in% inputRe[,1],
                                   "rectangle",
                                   "ellipse"),
                   node_font_size = ifelse(id %in% inputRe[,1],
                                   10,5),
                   node_height = ifelse(id %in% inputRe[,1],
                                   20,15))
      edges <- data.frame(id = paste0(inputRe[,1], "_", inputRe[,2]), source = inputRe[,1], target = inputRe[,2])
      
      cytoscape(nodes = nodes, edges = edges, elementId="networkfig")%>% 
        layout(name = 'cose',
               directed = TRUE,
               padding = 4, 
               avoidOverlapPadding = 30) %>%
        node_style('height' = 'data(node_height)',
                   'width' = 'data(node_height)',
                   'font-size' = 'data(node_font_size)',
                   'background-fit' = 'cover',
                   'border-color' = '#000',
                   'border-width' = 1,
                   'border-opacity' = 0.5,
                   'background-color' = 'data(node_color)',
                   'shape' = 'data(node_shape)') %>%
        edge_style('curve-style' = 'bezier',
                   'width' = 1,
                   'arrow-scale' = 0.8,
                   'target-arrow-shape' = 'triangle',
                   'line-color' = '#88898D',
                   'target-arrow-color' = '#88898D')%>%
          panzoom()
    }
}

```

### Information of Network {data-width=600}

```{r}
if(file.exists(tmp_path)){
  table_options <- function() {
    list(dom = 'Bfrtip',
      pageLength = 8,
      buttons = list(c('copy', 'csv', 'excel', 'pdf')),
      searchHighlight = TRUE,
      colReorder = TRUE,
      scrollX = TRUE,
      fixedColumns = TRUE,
      extensions = 'Responsive',
      deferRender = TRUE,
      scroller = TRUE,
      lengthChange = FALSE
      )
  }
  
  datatable(
    inputRaw,
    rownames = FALSE,
    editable = TRUE,
    elementId = "linktable",
    class = 'cell-border',
    escape = FALSE,
    options = table_options(),
    extensions = c('Buttons', 'Select')) %>% 
    formatStyle(columns = colnames(inputRaw), fontSize = '80%')
}
```

## {data-height=10}

<p class="one"></p>

Row
-----------------------------------

### The expression level of different types of isomiR {data-width=500}

```{r}
tmp_out <- paste0("data/", tmp_name, '.out')
if(file.exists(tmp_out)){
  iso_list <- read.table(tmp_out, sep = "\t", stringsAsFactors = F)
  iso_list <- iso_list[iso_list[,10]!="-", ]
  iso_list[,2] <- factor(iso_list[,2], levels = c("5p", "3p"))
  iso_list[,10] <- factor(iso_list[,10], levels = c("ref", "add5", "sub5", "add3", "sub3",
                                        "add5_add3", "add5_sub3", "sub5_add3", "sub5_sub3",
                                        "seed_snp", "tail_snp"))
  
  hchart(
    iso_list, 
    "column",
    hcaes(x=V10, y=V8, group = V2), color=c("#DE3025", "#257ADE")
    ) %>% 
    hc_xAxis(title = list(text = "")) %>% 
    hc_yAxis(title  = list(text = "TPM")) %>% 
    hc_tooltip(
      pointFormat = "{series.name}: <b>{point.y}</b><br/>", 
      shared = TRUE,
      valueSuffix = "", 
      crosshairs = TRUE
    ) %>% 
    hc_add_theme(hc_theme_flat(chart = list(backgroundColor = "#FFF")))%>% 
    hc_exporting(enabled = TRUE, filename = "different_types_of_isomiR")
}
```

